---
title: "Lab 01 - Hello R"
author: "Shatavia Bellmon"
date: "1/20/25"
output: 
  html_document: 
    fig_height: 3
    fig_width: 6
    highlight: espresso
    theme: paper
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
data("datasaurus_dozen")
```

?datasaurus_dozen

data("datasaurus_dozen")

```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print()
#> # A tibble: 13 × 2
#>    dataset        n
#>    <chr>      <int>
#>  1 away         142
#>  2 bullseye     142
#>  3 circle       142
#>  4 dino         142
#>  5 dots         142
#>  6 h_lines      142
#>  7 high_lines   142
#>  8 slant_down   142
#>  9 slant_up     142
#> 10 star         142
#> 11 v_lines      142
#> 12 wide_lines   142
#> 13 x_shape      142
```

## Exercises

### Exercise 1

2 columns, 1846 rows, and 3 variables

### Exercise 2

The answers for this exercise are already provided to help guide you. Clean up the narrative to reflect what you want to submit. Let’s break it into steps:

First, let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next, let's calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

``` {r}
dino_data %>%
  summarize(r = cor(x, y))
#> # A tibble: 1 × 1
#>         r
#>     <dbl>
#> 1 -0.0645
```


### Exercise 3

This is your turn to write the code and narrative for the star dataset. Follow the same steps as above to complete the analysis. Don't forget to label your chunks appropriately!

Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient.
To finish, clean up the narrative by removing these instructions.

```{r plot-star}
star_data<- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
``` {r}
star_data %>%
  summarize(r = cor(x, y))
#> # A tibble: 1 × 1
#>         r
#>     <dbl>
#> 1 -0.0630
```


There correlation coefficient for star is -0.630 and the dino correlation coefficients is -0.645.

### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r plot-circle}
circle_data<- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
``` {r}
circle_data %>%
  summarize(r = cor(x, y))
#> # A tibble: 1 × 1
#>         r
#>     <dbl>
#> 1 -0.0683
```
There correlation coefficient for circle is -0.683 and the dino correlation coefficients is -0.645.


### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!


